The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-06-08 docs/language_constraint_conll_camera_ready.tex
fixed the affiliation I think

\author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
  $^1$Computer Science \& Engineering, University of Washington, WA 98195, USA \\
  $^2$Allen Institute for Artificial Intelligence, WA 98103, USA \\
    {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
    \And \hspace{-2cm}Li Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A.~Smith$^1$ \\
  }

>>>>

\author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
  $^1$Paul G. Allen School of Computer Science \& Engineering, WA 98195, USA \\
  $^2$Allen Institute for Artificial Intelligence, WA 98103, USA \\
    {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
    \And \hspace{-2cm}Li Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A.~Smith$^1$ \\
  }
